PyEMMA: learning the ropes of Markov state modeling --- v\versionnumber

### 2018-07-20 manuscript.tex
minor changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{First steps with PyEMMA : v\versionnumber}

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}*]{Martin K. Scherer}
\author[1*]{Tim Hempel}
\author[1*]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}

@@

In addition to the literature on theory and application of MArkov state modeling~\cite{msm-book,buchete-msm-2008,noe-tmat-sampling,bowman-msm-2009,noe-folding-pathways,sarich-msm-quality,noe-fingerprints,noe-dy-neut-scatt,Chodera2014,ben-rev-msm,simon-mech-mod-nmr,oom-feliks}, we also recommend the literature on time-lagged independent component analysis (TICA)~\cite{tica,tica3,tica2,kinetic-maps}, transition path theory (TPT)~\cite{weinan-tpt,metzner-msm-tpt}, hidden Markov state models (HMMs)~\cite{noe-proj-hid-msm,hmm-baum-welch-alg,hmm-tutorial}, and variational techniques~\cite{noe-vac,vamp-preprint,gmrq}, as these topics play important roles within the standard MSM workflow.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{PyEMMA: learning the ropes of Markov state modeling --- v\versionnumber}

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}*]{Martin K. Scherer}
\author[1\authfn{1}*]{Tim Hempel}
\author[1*]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}

@@

In addition to the literature on theory and application of Markov state modeling~\cite{msm-book,buchete-msm-2008,noe-tmat-sampling,bowman-msm-2009,noe-folding-pathways,sarich-msm-quality,noe-fingerprints,noe-dy-neut-scatt,Chodera2014,ben-rev-msm,simon-mech-mod-nmr,oom-feliks}, we also recommend the literature on time-lagged independent component analysis (TICA)~\cite{tica,tica3,tica2,kinetic-maps}, transition path theory (TPT)~\cite{weinan-tpt,metzner-msm-tpt}, hidden Markov state models (HMMs)~\cite{noe-proj-hid-msm,hmm-baum-welch-alg,hmm-tutorial}, and variational techniques~\cite{noe-vac,vamp-preprint,gmrq}, as these topics play important roles within the standard MSM workflow.
